CommonMind Consortium: DLPFC

### 2020-09-21 combined_analysis/diff.networks.Rmd
Update diff networks

```{r recalibrate.null}
df_test_recal = apply_permutation_null( df_test_null )

@@

>>>>

```{r recalibrate.null, eval=FALSE}
df_test_recal = apply_permutation_null( df_test_null )

@@

# Discover clusters in first cohort
#----------------------------------
C = diff.net.Sex[[1]]
C.diff.discovery = C[[2]]^pwr - C[[1]]^pwr
C.diff.discovery = C.diff.discovery[keep.ensID,keep.ensID]
